---
title: "Inferential DA"
author: "Darius Kharazi"
date: "6/29/2018"
output: pdf_document
---

```{r setup, include = FALSE}
library(knitr)
library(ggplot2)
```

## Overview

There are two general hypotheses that we believe to be true:    
1. We believe that there are not generally different tooth lengths for each type of supplement.    
2. We believe that there are not generally different tooth lengths for each level of dose. 
    
Based on a 95% confidence interval, we decide to reject the null hypotheses and prefer the alternative hypotheses, since each p-value is extremely small. In other words, we believe that there are generally different tooth lengths for each type of supplement, and we believe that there are generally different tooth lengths for each level of dose.

## Appendix

```{r loaddata}
## Load the data
data <- ToothGrowth

## Look at a summary of the data
summary(data)

## Look at the data's structure
str(data)

## Look at some of the data's entries
head(data)

## Convert the numeric 'dose' variable to a factor variable
data$dose <- factor(data$dose)

## Boxplots of tooth length for different supplement types
with(data, boxplot(len~supp))

## Levels of tooth length
with(data, tapply(len, supp, mean))

## Boxplots of tooth length for different doses
with(data, boxplot(len~dose))

## Levels of dose
with(data, tapply(len, dose, mean))

## Boxplots of overall tooth length
ggplot(data, aes(dose, len, fill = dose)) +
  facet_grid(.~supp, labeller = as_labeller(c("OJ" = "Orange Juice", "VC" = "Ascorbic Acid"))) +
  labs(title = "The Effect of Vitamin C on Tooth Grown in Guinea Pigs",
       x = "Dose (mg/day)",
       y = "Tooth Length (cm)") +
  scale_fill_discrete(name = "Dose") +
  geom_boxplot()

## Two sample t-test between different supplement types
oj <- with(data, len[supp == "OJ"])
vc <- with(data, len[supp == "VC"])
t.test(oj, vc, alternative = "greater") # reject the null hypothesis

## Two sample t-test between different levels of doses
half <- with(data, len[dose == 0.5])
one <- with(data, len[dose == 1])
two <- with(data, len[dose == 2])
t.test(one, half, alternative = "greater") # reject the null hypothesis
t.test(two, one, alternative = "greater") # reject the null hypothesis
t.test(two, half, alternative = "greater") # reject the null hypothesis
```
